Paper figures

### 2020-09-26 notebooks/paper_plots_0909.Rmd
separated scatter plots from randomizations

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
with open(f'data/interim/yuri/yuri.pickle','rb') as f:
    e_yuri = pickle.load(f)
with open(f'data/interim/huri/huri.pickle','rb') as f:
    e_huri = pickle.load(f)

pcc_df = e_pcc.df
yuri_df = e_yuri.df
huri_df = e_huri.df
```

```{r}
pcc_df = py$pcc_df
yuri_df = py$yuri_df
huri_df = py$huri_df
library(tidyverse)
library(cowplot)
library(ggpubr)
```

```{r}
p1 = ggplot(pcc_df, aes(x=deg,y=eff))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Effectiveness')+
    stat_cor(method='pearson')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
p2 = ggplot(pcc_df, aes(x=deg,y=sens))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Sensitivity')+
    stat_cor(method='spearman')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
lgn = cowplot::get_legend(p2)

plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn, nrow=1, labels=c('A','B',''))

@@

p3 = combined_rewire_df%>%
    ggplot(aes(x=data,y=eff_deg_pearson,color=type))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_point(position=position_jitterdodge(dodge.width=0.9), aes(shape=data))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    xlab('')+ylab('Effectiveness degree correlation')+
    theme_bw()+
    theme(axis.text.x=element_blank())
p4 = combined_rewire_df%>%
    ggplot(aes(x=data,y=sens_deg_spearman,color=type))+
#    geom_boxplot()+
#    geom_jitter(aes(color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    geom_point(position=position_jitterdodge(dodge.width=0.9), aes(shape=data))+
    xlab('')+ylab('Sensitivity degree correlation')+
    theme_bw()+
    theme(axis.text.x=element_blank())+
    scale_shape_discrete(labels=network_labels)+
    scale_color_discrete(labels=c('Rewired network', 'Real network'))

lgn34  <- cowplot::get_legend(p4)
    theme(axis.text.x=element_blank())
plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn,
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=2, labels=c('A','B','','C','D',''))
ggsave('tmp.png')
```

@@

auc_plot <- auc_data%>%
    ggplot(aes(x=variable_0,y=r))+
    geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
    geom_line(aes(group=group),color='grey')+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    theme_bw()+
    ylab("AUC")+
    xlab("Deletion parameter")+
    labs(color = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
    scale_colour_brewer(palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='right')

deletion_plot <- deletion_df %>% mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
    ggplot(aes(x=range, y= gc_size, color = variable_0  ))+
#    geom_point(size=1)+
        geom_line()+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('Ratio of deleted nodes')+
    ylab('Giant component ratio')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    theme_bw()+
    theme(legend.position='right')

deletion_lgn <- cowplot::get_legend(auc_plot)
plot_grid(deletion_plot+    theme(legend.position='')
, auc_plot+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.45, 0.45,.1), labels=c('A','B'))
ggsave('tmp.png',width=12)

@@

>>>>

with open(f'data/interim/pcc_0909/pcc.pickle','rb') as f:
    e_pcc = pickle.load(f)
with open(f'data/interim/yuri_0916/yuri.pickle','rb') as f:
    e_yuri = pickle.load(f)
with open(f'data/interim/huri_0916/huri.pickle','rb') as f:
    e_huri = pickle.load(f)

pcc_df = e_pcc.df
pcc_gc = e_pcc.graph_gc
pcc_gc_pos = (dict(pcc_gc.nodes(data='pos')))
yuri_df = e_yuri.df
huri_df = e_huri.df
```

```{r}
library(tidyverse)
library(cowplot)
library(ggpubr)

pcc_df = py$pcc_df%>%mutate(data='pcc')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
yuri_df = py$yuri_df%>%mutate(data='yuri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))
huri_df = py$huri_df%>%mutate(data='huri')%>%mutate(sens_norm = sens/nrow(.),eff_norm = eff/nrow(.))

combined_df = bind_rows(pcc_df, yuri_df,huri_df)%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))
```

```{r}
p1 = ggplot(pcc_df, aes(x=deg,y=eff_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Effectiveness')+
    stat_cor(method='pearson')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()
p2 = ggplot(pcc_df, aes(x=deg,y=sens_norm))+
    geom_point(aes(color=cat_))+
    xlab('Degree')+
    ylab('Sensitivity')+
    stat_cor(method='spearman')   +
    guides(color=guide_legend(title="Experiment categories"))+
    theme_bw()+theme(legend.text = element_text(margin = margin(t=5, b = 5, unit = "pt")))
lgn = cowplot::get_legend(p2)
fig3 = plot_grid(p1+theme(legend.position=''),
          p2+theme(legend.position=''),
          lgn, nrow=1, labels=c('A','B',''),rel_widths=c(0.4,0.4,0.2))
ggsave('reports/figures/paper_figures_0916/fig3.png', fig3, width=8,height=6)
```

@@

p3 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=eff_deg_pearson,color=type, y=..scaled..),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=eff_deg_pearson,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Effectiveness degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"))+
    scale_y_continuous(expand = c(0, 0)) 
p4 = 
    ggplot()+
    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
#    geom_boxplot()+
#    geom_jitter()+
    geom_density(data =combined_rewire_df%>%filter(type!='real'),aes(x=sens_deg_spearman,y=..scaled..,color=type),linetype = "dashed")+
    geom_vline(data =combined_rewire_df%>%filter(type=='real'),aes(xintercept=sens_deg_spearman,color=type))+
    guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    ylab('Density')+xlab('Sensitivity degree correlation')+
    theme_bw()+
    theme(panel.spacing = unit(2, "lines"),legend.position='bottom')+
    scale_color_discrete(labels=c('Rewired networks', 'Real networks'))+
    scale_y_continuous(expand = c(0, 0)) 
lgn34  <- cowplot::get_legend(p4)
plot_grid(
          p3+theme(legend.position=''),
 p4+theme(legend.position=''), lgn34,
 nrow=3, labels=c('A','B','','C','D',''), rel_heights = c(0.45,0.45,0.1))
ggsave('reports/figures/paper_figures_0916/fig2.png',width=7)
```

@@

auc_plot <- auc_data%>%
    ggplot(aes(x=variable_0,y=auc))+
    geom_bar(aes(fill=variable_0),stat='identity')+
 #   geom_point(aes(color=variable_0))+#, position=position_jitterdodge())+
#    geom_line(aes(group=group),color='grey')+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    theme_bw()+
    ylab("Robustness")+
    xlab("Deletion parameter")+
    labs(fill = "Deletion\nparameter")+
    scale_x_discrete(labels = c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
    scale_fill_brewer(palette = "Set1", labels= c(
                                "Degree",
                                "Betweenness",
                                "Effectiveness",
                                "Closeness",
                                "Eigencentrality",
                                "Random",
                                "Sensitivity"))+
   theme(legend.position='right')

#combined_df %>% group_by(data)%>%summarise(deg_btw = cor(deg, btw),
#                                           deg_eff = cor(deg,eff),
#                                           deg_sens = cor(deg,sens),
#                                           deg_eigen = cor(deg, eigenvec_centr),
#                                           deg_closeness = cor(deg, closeness_centr))
deletion_plot <- deletion_df %>% mutate(variable_0 = fct_relevel(variable_0, levels(auc_data$variable_0)))%>%
    ggplot(aes(x=range, y= gc_size, color = variable_0  ))+
#    geom_point(size=1)+
        geom_line()+
    facet_grid(rows = vars(group), labeller = labeller(group=facet_labels))+
    scale_colour_brewer(palette = "Set1")+ 
    xlab('% Deleted Nodes')+
    ylab('% Giant Component Size')+
    scale_y_continuous(labels = scales::percent)+
    scale_x_continuous(labels = scales::percent)+
    theme_bw()+
    theme(legend.position='right')

deletion_lgn <- cowplot::get_legend(auc_plot)
plot_grid(deletion_plot+    theme(legend.position='')
, auc_plot+    theme(legend.position='')
,deletion_lgn, nrow=1, rel_widths =c(0.4, 0.5,.1), labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig4.png',width=12)

@@

# Sensor connectivity and neighbor degree
```{r}
sensor_connectivity_df <- read_csv('data/interim/sensor_connectivity_0915/sensor_connectivity_df.csv')%>%
    mutate(data= fct_relevel(data, c('pcc','yuri','huri')))

#library(ggridges)

#sensor_connectivity_df %>%
#    filter(type=='random')%>%
#    ggplot(aes(x=ratio,y=data))+
##    facet_grid(rows=vars(data))+
##    geom_histogram(bins=50)
#    geom_density_ridges()
#ggsave('tmp.png',width=12)

#p3 = 
sensor_connectivity_plot <- 
    ggplot()+
    geom_boxplot(data=sensor_connectivity_df%>%filter(type=='random'),
                 aes(x=data,y=ratio,color=type))+
#    geom_jitter()+
    geom_point(data=sensor_connectivity_df%>%filter(type=='real'),
            aes(x=data,y=ratio,color=type, group=data))+
               #position=position_jitter(), aes(shape=data))+
    scale_color_discrete(labels=c('Random sampled set', 'Sensors'))+
    scale_x_discrete(labels=network_labels)+
  guides(color=guide_legend(title="Data type"),shape=guide_legend(title="Network type"))+
    xlab('Network type')+ylab('Ratio of between group edges\nto outgroup edges')+
    theme_bw()
neighbor_degree_plot <- combined_df%>%
    ggplot(aes(x=sens_norm,y=neighbor_degree))+
    facet_grid(cols=vars(data),labeller = labeller(data=facet_labels))+
    geom_point()+
    theme_bw()+
    ylab('Average neighbor degree')+
    xlab('Sensitivity')
plot_grid(neighbor_degree_plot, sensor_connectivity_plot, nrow=2 , labels=c('A','B'))
ggsave('reports/figures/paper_figures_0916/fig5.png')

```{r}
convert_networkx_to_igraph <- 			# 
    function
(
 	nx_object,
    df
)
{
    nx =  reticulate::import("networkx")
    ig = igraph::graph.adjacency(nx$adjacency_matrix(nx_object), mode = 'undirected')
    #ig = igraph::set_vertex_attr(ig , name =  'orf_name', value  = (df$orf_name))
    ig = igraph::set_vertex_attr(ig , name =  'name', value  = (df$orf_name))
    #igraph::set_vertex_attr(ig, "pos", nx_object$nodes('pos'))
    ig
}
```
```{r}
plot_network_spring <- 			# 
    function
(
    gc , df , pos , ... 	
)
{
 pcc_gc_ig = convert_networkx_to_igraph(gc, df)

png('tmp.png')
plot(pcc_gc_ig, vertex.size=1, vertex.label=NA, layout = pos)
dev.off()

}
pcc_gc = py$pcc_gc
pcc_gc_pos = matrix(unlist(py$pcc_gc_pos),ncol=2,byrow=TRUE)

pcc_gc_ig = convert_networkx_to_igraph(pcc_gc, pcc_df)

get_subnetwork  <- function(gc, subset){
    sub_gc_nodes = igraph::ego(gc, nodes= subset)%>%unlist%>%unique

    sub_gc  <- igraph::induced_subgraph(gc, sub_gc_nodes)

    sub_gc
}

pcc_sensors = pcc_df %>% filter(sens>quantile(sens,0.99))
pcc_sensor_sub = get_subnetwork(pcc_gc_ig, pcc_sensors$orf_name)
#plot_network_spring(pcc_gc, pcc_df, pcc_gc_pos)

png('tmp.png', res=150, height=3, width=3,units='in')
plot(pcc_sensor_sub, vertex.size = 2 , vertex.color = 'white', vertex.label.color='black',vertex.label.size=8, vertex.label.cex = 0.4, layout=igraph::layout.fruchterman.reingold)
dev.off()
```
